\thesistitle

### 2019-07-19 sections/background.tex
Move method

\subsection{Extract Method}
Method extraction is one of the most used methods of refactoring duplication in source code. Several studies have already concluded that most duplication in source code is found in the body of methods \ref{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality between methods to a common place: a new method.

@@

>>>>

\subsection{Extract Method}
Method extraction is one of the most used methods of refactoring duplication in source code. Several studies have already concluded that most duplication in source code is found in the body of methods \ref{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality between methods to a common place: a new method. An example of this procedure is displayed in figure \ref{fig:extractmethod}.

@@

\subsection{Move method}
In the example of the previous section, both duplicated parts are in the same method. However, a study by Fontana et al. \ref{fontana2015duplicated} shows that this is most often not the case. Based on the relation between clone instances, the extracted method must be moved to be accessible by all locations of the clone instances. This might require different techniques.

\subsubsection{Pull up method}
A refactoring technique to move a method up in its inheritance structure is called ``Pull up method'' \ref{fowler2018refactoring}. This way, if cloned methods are related in any way through inheritance, they can be called by both classes by placing the method in a class they both have in common. This way its possible to refactor both fully cloned methods (by just pulling up the method) and partially cloned methods (by first performing method extraction and then pulling up the refactored method).

\subsubsection{Create class abstraction based on implicit relations}
\todo{}
